---
title: "Final Project"
subtitle: "Data Science for Biologists, Spring 2021"
author: "Lalita Martin"
output: 
  html_document: 
    theme: cosmo
    highlight: pygments
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
# DON'T CHANGE THE NEXT LINE, except to add NEW options if you have any.
knitr::opts_chunk$set(warning=FALSE, message=FALSE, echo = TRUE, include = TRUE)

# Load all libraries you use HERE:
library(tidyverse)
library(dplyr)
```

<br><br>

## Introduction

```{r read-examine-data}
#set file path
parks_file <- file.path("martin_parks.csv")
species_file <- file.path("martin_species.csv")
#read in datasets
parks <-read_csv(parks_file)
species <- read_csv(species_file)
#glimpse parks and species datasets
glimpse(parks)
glimpse(species)
```

<br><br>

## Question 1

#### REPLACE TEXT WITH YOUR QUESTION. Your question should literally be a level-4 header.

### Methods

```{methods}


```

### Answer

Replace this text with your answer to your question.


<br><br>

## Question 2

#### REPLACE TEXT WITH YOUR QUESTION. Your question should literally be a level-4 header.

### Methods

```{methods}


```

### Answer

Replace this text with your answer to your question.

<br><br>

## Question 3

#### REPLACE TEXT WITH YOUR QUESTION. Your question should literally be a level-4 header.

### Methods

```{methods}


```

### Answer

Replace this text with your answer to your question.


<br><br>

## Question 4

#### REPLACE TEXT WITH YOUR QUESTION. Your question should literally be a level-4 header.

### Methods

```{methods}


```

### Answer

Replace this text with your answer to your question.
