---
title: "Final Project"
subtitle: "Data Science for Biologists, Spring 2021"
author: "Lalita Martin"
output: 
  html_document: 
    theme: cosmo
    highlight: pygments
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
# DON'T CHANGE THE NEXT LINE, except to add NEW options if you have any.
knitr::opts_chunk$set(warning=FALSE, message=FALSE, echo = TRUE, include = TRUE)

# Load all libraries you use HERE:
library(tidyverse)
library(dplyr)
```

<br><br>

## Introduction

The datasets I have chosen are the [National Parks Biodiversity](https://www.kaggle.com/nationalparkservice/park-biodiversity) datasets from Kaggle. They are about National Parks and the species of various organisms found in these parks. I chose these datasets because I want to be a biologist on some level and I enjoy looking at biodiversity all over the world. These datasets show species diversity in various national parks, which I also like, as I have a great interest in working for the parks dept. one day. 

```{r read-examine-data}
#set file path
parks_file <- file.path("martin_parks.csv")
species_file <- file.path("martin_species.csv")
#read in datasets
parks <-read_csv(parks_file)
species <- read_csv(species_file)
#glimpse parks and species datasets
glimpse(parks)
glimpse(species)
```

<br><br>

## Question 1

#### Which state has the largest (in acres) state park? 

### Methods

```{r methods1}
parks %>% 
  #let's work with only the parks that are solely in one state
  filter(str_detect(State, ",", negate=TRUE)) -> parks_clean # removes rows with , in State column

#Lets take some parks to compare
parks_clean %>%
  filter(Acres > 1000000) %>%
  arrange(-Acres) -> big_parks
big_parks

ggplot(big_parks)+
  aes(x = State, y = Acres, fill = State)+
  scale_y_log10()+
  geom_col()+
  labs(title = "National Park Acreage Per State")+
  theme_grey()
```

**Arkansas** comes in first with *Wrangell - St. Elias National Park and Preserve* at a whopping 8,323,148 acres! 


<br><br>

## Question 2

#### Which parks have the most fungi species growing in them?

### Methods

```{r methods2}
species %>%
  rename(park_name = `Park Name`) %>%
  filter(Category == "Fungi") %>%
  filter(Occurrence == "Present") %>%
  count(park_name) %>%
  filter(n > 200) %>%
  arrange(-n) -> fun_guy
fun_guy

ggplot(fun_guy)+
  aes(y = reorder(park_name, n), x = n, fill = park_name)+
  geom_col()+
  theme_grey()+
  theme(legend.position = "none")+
  labs(title = "Number of Fungi Species in Parks", 
       x = "Number of Species Found", 
       y = "Park Name")
```

### Answer

**Shenandoah National Park** has the most species of fungi, followed by Great Smoky Mountains, North Cascades National Park, and three others all with more than 200 species found! 

<br><br>

## Question 3

#### Which parks have the greatest amounts of algae species? 

### Methods

```{r methods3}
species %>%
  rename(park_name = `Park Name`) %>%
  filter(Category == "Algae") %>%
  filter(Occurrence == "Present") %>%
  count(park_name) %>%
  filter(n > 50) %>%
  arrange(-n) -> gee_al
gee_al

ggplot(gee_al)+
  aes(y = reorder(park_name, n), x = n, fill = park_name)+
  geom_col()+
  theme_grey()+
  theme(legend.position = "none")+
  labs(title = "Number of Algae Species in Parks", 
       x = "Number of Species Found",  
       y = "Park Name")
```

### Answer

Rocky Mountain National Park had the highest amount of reported algae species of **150!** Followed by Congaree with **74**, Channel Islands at **61** and Glacier Bay at **57.** 


<br><br>

## Question 4

#### How many _different_ vascular plants are in Death Valley compared to The Great Smoky Mountain National Park?
### Methods

```{r methods4}
species %>%
  rename(park_name = `Park Name`) %>%
  rename(sci_name = `Scientific Name`) %>%
  rename(common_name = `Common Names`) %>%
  filter(Category == "Vascular Plant") %>%
  filter(park_name == c("Death Valley National Park", "Great Smoky Mountains National Park")) %>%
  filter(Occurrence == "Present") %>% 
  count(park_name)-> plants
plants

ggplot(plants)+
  aes(x = reorder(park_name, n), y = n, fill = park_name)+
  geom_col()+
  theme_grey()+
  theme(legend.position = "none")+
  labs(title = "Vascular Plant Comparison of Death Valley and GSMNP", 
       y = "Number of Species Found",  
       x = "Park Name")
```

### Answer

In Death Valley, there are **491** species of vascular plant and in the GSMNP there are **818.** 
